Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-06 paper/main.tex
motivating example

>>>>

\begin{figure}
\begin{verbatim}
year = int(time.strftime("%Y"))
age = input("Enter your age")
print("You will be twice as old in:")
print(year + age)
\end{verbatim}
\caption{A buggy program}
\end{figure}

Consider the program in Fig. 1, adapted from our dataset. The program
attempts to use the current year and the user's age to compute their
birth year and the year they can vote. However, while line 1 correctly
turns the current year from a string into an int, this `int' call is
missing from line 2 so `age' remains a string, and thus the addition
on line 4 causes the program to crash.

Notice that while a correct fix (and the one that the programmer
actually used) is to add an `int' call to line 2, another possible ``fix''
would be to \textit{remove} the `int' call from line 1 - both year and
age would then be strings, and the addition on line 4 would be interpreted
as string concatenation. This shows the necessity of a heuristic, data-driven
approach, since without test cases there is no way to tell for sure which
fix is better.

We can also start to see some features which will be
important for finding bugs: we will need the \textit{type} of age, as
well as some \textit{contextual} information about how it's used in the program.

% TODO: would also be nice if the example showed that the place Python crashes
% may not be a place that should be fixed?
